Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-06-05 article.tex
start filtering section
describe linear filters

% Introduce filtering
\section{Signal filtering methodology}

@@

>>>>

\section{Signal filtering methodology}

% Explain why we need to filter
% TODO

% Filtering methodology
Prior inferring the network, the fluorescent calicum time series are smoothed
using several linear and non linear filters. A low-pass filter is first applied
for all valid value of $t$
\[
X^\prime_{t,i} = \sum_{l=-3}^2 a_l X_{t+l,i} \forall i
\]
where the $a_l$ coefficient were taken in one of the four following tuples:
$(\left\{a_l\right\}_{l=-3}^2)=(0, 0, 1, 1, 1, 1)$,
$(\left\{a_l\right\}_{l=-3}^2)=(0, 0, 1, 1, 1, 0)$,
$(\left\{a_l\right\}_{l=-3}^2)=(1, 1, 1, 1, 0, 0)$ or
$(\left\{a_l\right\}_{l=-3}^2)=(0.4, 0.8, 1, 1, 0, 0)$.

The next step is to apply a high-pass filter to the signal:
\[
X^{\prime\prime}_{t,i} = X^{\prime}_{t,i} - X^{\prime}_{t-1,i}
\forall i, \forall t \in \left\{2, \ldots, n\right\}
\]

5 kinds
of filtering technique: (i) a low pass filter, (ii) a high pass filter, (iii)
a high thresholding filter

@@

% There are 4 filters:
%     1/ smoothing filter (see filtering argument)
%     2/ hard thresholding filter (see threshold argument)
%     3/ non-linear filter: x[i] = x[i] ** 0.9
%     4/ non-linear filter based on the neuron activations

 %  X_new = np.diff(X_new, axis=0)
 %  thresh1 = X_new < threshold * 1
 %  thresh2 = X_new >= threshold * 1
 %  X_new[thresh1] = 0
 %  X_new[thresh2] = pow(X_new[thresh2], 0.9)
